---
title: "Shiny App and Repro Pitch"
author: "Benjamin Eggart"
date: "24 8 2021"
output:
  slidy_presentation: default
  ioslides_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Oktoberfest Analysis Report

Oktoberfest Data Analysis Report enabled developing data products using shiny apps being embedded within RMarkDown.

Using PageLeft and PageRight keys all the slides can be traversed.

## Application Overview

- Relevant Data like beer price, chicken consumption or visitors can be chosen
- A year can be selected to predict the future value based on a linear regression model
- This Report explains the usage of the app


## Slide with Complete Reporting Appliaction

Click the Below Link for the Application.

https://oktoberfestpredictor.shinyapps.io/Shiny-Application-and-Reproducible-Pitch/

Click the link below for compiled project files on github repo.

https://github.com/beggart/Shiny-Application-and-Reproducible-Pitch

## Data Used
The data used for this application is a Oktoberfest data set Containing information about the duration *dauer*, visitors in total *besucher_gesamt*, visitors maximum during Oktoberfest *besucher_tag*, beer price *bier_preis*, beer consumption *bier_konsum*, chicken price *hendl_preis* and chicken consumption *hendl_konsum* for the years of 1985 to 2019.

The data is open source and available from the city of Munich https://www.opengov-muenchen.de/ 

```{r, echo=TRUE}
beer_data <- data.table::fread(input = "https://www.opengov-muenchen.de/dataset/8d6c8251-7956-4f92-8c96-f79106aab828/resource/e0f664cf-6dd9-4743-bd2b-81a8b18bd1d2/download/oktoberfestgesamt19852019.csv"
                               , na.strings="?"
)
head(beer_data)
```

