---
title: "Shiny App and Repro Pitch"
author: "Benjamin Eggart"
date: "24 8 2021"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Oktoberfest Analysis Report

Oktoberfest Data Analysis Report enabled developing data products using shiny apps being embedded within RMarkDown.

Using PageUp and PageDown keys all the slides can be traversed.

## Application Overview

- Relevant Data like beer price, chicken consumption or visitors can be chosen
- A year can be selected to predict the future value based on a linear regression model
- This Report explains the usage of the app


## Slide with Complete Reporting Appliaction

Click the Below Link for the Application.

https://oktoberfestpredictor.shinyapps.io/Shiny-Application-and-Reproducible-Pitch/

Click the link below for compiled project files on gitub repo.

https://github.com/beggart/Shiny-Application-and-Reproducible-Pitch

## Data Used
The data used for this application is a Oktoberfest data set Containing information about 53940 diamonds with 10 variables.

```{r, echo=TRUE}
beer_data <- data.table::fread(input = "https://www.opengov-muenchen.de/dataset/8d6c8251-7956-4f92-8c96-f79106aab828/resource/e0f664cf-6dd9-4743-bd2b-81a8b18bd1d2/download/oktoberfestgesamt19852019.csv"
                               , na.strings="?"
)
head(beer_data)
```

